\chapter{INTRODUCTION}% Chapter titles are capitalized -- UNLV rule.

Writing a graduate thesis is very time consuming.  One of the
obstacles placed in front of the student is the set of
requirements for the look of thesis.  These requirements look like
they date from the middle ages, but there's nothing you or I can
do about that.  Writing a thesis in mathematics or some other
discipline that requires mathematical symbols is even more
difficult, because most typesetting programs do not deal with them
very well.  One program that was designed to handle mathematical
symbols is \LaTeX.  This program is a publishing grade program.
For example, I have published a book that was typeset using \LaTeX
\cite{B1} and almost all journals that I submit to request that
source files be in \LaTeX.

Unfortunately, \LaTeX\ is much more sophisticated than what the
average graduate student requires, and none of its standard
packages look anything like the required UNLV format (though every
one of them looks better). On the other hand, much of this can be
automated by a \TeX\! pert. That's what this package is about.  It
describes how to use the UNLVthesis.sty style file to format
theses into the UNLV format. Unfortunately, I do not make the
rules, so there may be things I haven't anticipated or dealt with
correctly, so some tweaking may be required.  I welcome questions,
though I may not deal with them promptly.  I can be reached at
baragar@unlv.edu.

There are some requirements that are very difficult to adhere to.
For example, the font style is to be ``a standard ... computer
font, such as Bookman, Courier, Arial(Helvetica), or Times.''
Though it is possible to change the font in \LaTeX\ documents, I
prefer to not do so.  The \LaTeX\ font is Computer Modern Roman,
and very few would notice that it is not Times.
